Stage-Splitting a Modal Language

### 2014-08-06 paper/splitting.tex
added a paragraph and figure on the output language

The basic idea is that we want to take a term which contains interleaved stage \bbone\ and stage \bbtwo\ code
and untangle it into two separate terms: one with all of the stage \bbone\ code and one with all the stage \bbtwo\ code.
To facilitate communication between the stages, there is a data structure passed between the stages, 
which is an output of the stage \bbone\ term and and input to the stage \bbtwo\ term.

>>>>

The basic idea is that we want to take a term which contains interleaved stage \bbone\ and stage \bbtwo\ code
and split it into two separate terms: one with all of the stage \bbone\ code and one with all the stage \bbtwo\ code.
To facilitate communication between the stages, there is a data structure passed between the stages, 
which is an output of the stage \bbone\ term and and input to the stage \bbtwo\ term.

The input to our splitting algorithm is a term in \lang, and the output is two terms in \langmono, an
unstaged language.  The grammar for \langmono is given in \ref{fig:monoGrammar}.  It has no
staging features (we say that implicitly it has only one stage), and it is untyped.  
Modulo these differences, \langmono has all of the same features as \lang, 
although this is a matter of taste
\footnote{Since \lang is untyped, we could encode everything with just functions.}.
